Title Goes Here

### 2020-04-17 analysis/paper/paper.Rmd
Citation and do the topic model

```{r}
# let's run the topic model fn for each conf
CAA18_tm <- do_the_topic_model(CAA18)
xxx_tm <- do_the_topic_model(xxx)
xxx_tm <- do_the_topic_model(xxx)

# Let's save the output for each one
saveRDS(CAA18_tm, here::here("analysis/data/derived-data/CAA18_topic_model.rds"))
saveRDS(xxx_tm, here::here("analysis/data/derived-data/xxx_topic_model.rds"))
saveRDS(xxx_tm, here::here("analysis/data/derived-data/xxx_topic_model.rds"))
```

>>>>

```{r}
# let's run the topic model fn for each conf
CAA18_tm <- do_the_topic_model(CAA18, 21)
EAA18_tm <- do_the_topic_model(EAA18, 12)
SAA18_tm <- do_the_topic_model(SAA18, 21)

# Let's save the output for each one
saveRDS(CAA18_tm, here::here("analysis/data/derived-data/CAA18_topic_model.rds"))
saveRDS(EAA18_tm, here::here("analysis/data/derived-data/EAA18_topic_model.rds"))
saveRDS(SAA18_tm, here::here("analysis/data/derived-data/SAA18_topic_model.rds"))
```
